Lyman-$\alpha$ photons through rotating outflows

### 2018-03-27 paper/paper.tex
edit
edita

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode\mathrm \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Outflows and rotation in LAEs]{Lyman-alpha spectra from
  rotating outflows}
\author[M.C. Remolina-Gutierrez \& J.E. Forero-Romero]{
  Maria Camila Remolina-Guti\'errez$^{1}$
  \thanks{mc.remolina197@uniandes.edu.co} \&
  Jaime E. Forero-Romero $^{1}$
  \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^{1}$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      \tauh & \vrot (\kms) & \vout (\kms) \\
      \hline
      $10^5$ & \{0\} & \{5, 25, 50\} \\
      $10^6$ & \{0\} & \{5, 25, 50\}\\
      $10^7$ & \{0\} & \{5, 25, 50\}\\
      $10^5$ & \{50, 100\} & \{25, 50, 75\} \\
      $10^6$ & \{50, 100\} & \{25, 50, 75\}\\
      $10^7$ & \{50, 100\} & \{25, 50, 75\}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    \tauh, \vrot and \vout are used.}
  \label{tab:values}
\end{table}

@@

\begin{equation}
x' = x + \frac{\vec{v}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

Figure \ref{fig:doppler_shift} summarizes the most important trends of
our simulations.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Doppler shift effect:} We fixed $\tauh=10^6$ and $\theta=90^\circ$.
  	We vary \vrot increasing from left to right and \vout increasing from top to
  	bottom. The legend represents the \lya line obtained if there is no rotation
  	(in thin line), if there is a radiative transfer of rotation and outflows
  	(thick and clear line), and if there is a radiative transfer of only outflows,
  	but also a Doppler shift from the rotational velocity (thick and dark line).
	    \label{fig:doppler_shift}}
\end{figure*}

\subsection{Monte-Carlo Radiative Transfer Model}

We evaluate the effects of increasing rotational
velocity at fixed values of the optical depth and outflows velocity.
Figure \ref{fig:varying_rotation_small} summarizes its behavior
(for a largest range see Figure \ref{fig:varying_rotation}).
All plots correspond to the same outflows velocity of $\vout=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

% Esta figura deberia tener 2 x 2 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% | tau=1E5, vrot=50, | tau=1E5, vrot=100 |
% | tau=1E6, vrot=50, | tau=1E6, vrot=100 |
%\begin{figure*}
%  \begin{center}
%    \includegraphics[width=0.90\textwidth]{./figures/results/varying_rotation_small}
%  \end{center}
%  \caption{\textbf{Spectra for fixed outflows velocity:} We fixed $\vout=50$\kms.
%    We vary \vrot increasing from left to right, \tauh increasing from top to
%    bottom, and $\theta$ according to the legend.
%    \label{fig:varying_rotation_small}}
%\end{figure*}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm V_{\mathrm{rot}}\else $V_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm V_{\mathrm{out}}\else $V_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode\mathrm \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Outflows and rotation in LAEs]{Lyman-$\alpha$ photons through rotating outflows}
\author[M.C. Remolina-Gutierrez \& J.E. Forero-Romero]{
  Maria Camila Remolina-Guti\'errez$^{1}$
  \thanks{mc.remolina197@uniandes.edu.co} \&
  Jaime E. Forero-Romero $^{1}$
  \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^{1}$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      \tauh & \vrot (\kms) & \vout (\kms) \\
      \hline
      \{$10^5$, $10^6$, $10^7$\}  & \{0, 50, 100\} & \{5, 25, 50\} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    \tauh, \vrot and \vout are used.}
  \label{tab:values}
\end{table}

@@

\begin{equation}
x' = x + \frac{\vec{V}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

\subsection{Qualitative Trends}
\label{sec:qualitative}
Figure \ref{fig:doppler_shift} summarizes the most important trends of
our simulations. 
The six panels correspond to $\tau=10^6$ and a viewing angle of
$\theta =90^{\deg}$, that is perpendicular to the rotation axis of the
galaxy. 
In every panel the thin black line corresponds to the pure outflow
solution (i.e. without rotation). 
From top to bottom we see the effect of increasing the outflow
velocity, which is the expected increasing asymmetry towards the red
peak.

The thick black line corresponds to the solution that includes both
outflows and rotation.
Comparing the left and right columns (lower versus higher rotational
velocity) we can see two immediate effects.
First, the line broadens and second, the intensity at the line's
center increases.

Finally, the thick gray line correspods to the pure outflow solution
with the Doppler boost added to model rotation's influence.
In all cases the Doppler boost does a good job at capturing the broad
morphological features introduced by rotation: the angle dependence,
the broadening and the intensity increase at the line's center.

In Figure \ref{fig:angle_influence} we show the same results as in
Figure \ref{fig:doppler_shift} but for a viewing angle of $\theta =
90^{\deg}$, that is parallel to the rotation axis. 
In this case we see that the effect of rotation is very hard to see. 
As \ref{Garavito14} showed, pure rotation introduces a strong
dependence with viewing angle, a trend that we find also holds for
rotation mixed with ouflows.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing from top to
    bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of only outflows,
    but also a Doppler shift from the rotational velocity (thick and dark line).
    \label{fig:doppler_shift}}
\end{figure*}

\subsection{Quantitative trends}
\label{sec:quantitative}

After finding the qualitative influence of the different parameters.
